Unshuffling Permutations

### 2015-09-14 article.tex
conclusion

>>>>

There are a number of further directions of investigation in this general subject.
We mention several -~not necessarily new~- open problems that are, in our opinion,
the most interesting.
How many permutations of $S_{2n}$ are squares?
How many $(213,231)$-avoiding permutations of $S_{2n}$ are squares?
(Equivalentely, how many binary strings of length $2n$ are squares;
see Problem~4 in \cite{Henshall:Rampersad:Shallit:2011})?
How hard is the problem of deciding whether a $(213,231)$-avoiding permutation
is a square (see Problem~4 in \cite{Henshall:Rampersad:Shallit:2011})?)
Given two permutations $\pi$ and $\sigma$, how hard is the problem of deciding
whether $\pi$ is the union of two patterns order-isomorphic to $\sigma$?
